Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-21 PNAS/index.Rnw
updates and intro

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1,2]{Susan Vanderplas}
\author[b,1]{Heike Hofmann}
\author[b]{Alicia Carriquiry}

\affil[a]{Statistics Department, University of Nebraska Lincoln. 350 Hardin Hall, 3310 Holdrege North Wing, Lincoln, NE 68503}
\affil[b]{Affiliation Two}
\affil[c]{Affiliation Three}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) contributed equally to this work with A.T. (Author Two) (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: susan.vanderplas@unl.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

@@

Note: please start your introduction without including the word ``Introduction'' as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraph.

\section*{Guide to using this template on Overleaf}

Please note that whilst this template provides a preview of the typeset manuscript for submission, to help in this preparation, it will not necessarily be the final publication layout. For more detailed information please see the \href{ https://www.pnas.org/page/authors/format}{PNAS Information for Authors}.

If you have a question while using this template on Overleaf, please use the help menu (``?'') on the top bar to search for \href{https://www.overleaf.com/help}{help and tutorials}. You can also \href{https://www.overleaf.com/contact}{contact the Overleaf support team} at any time with specific questions about your manuscript or feedback on the template.

\subsection*{Author Affiliations}

Include department, institution, and complete address, with the ZIP/postal code, for each author. Use lower case letters to match authors with institutions, as shown in the example. PNAS strongly encourages authors to supply an \href{https://orcid.org/}{ORCID identifier} for each author. Individual authors must link their ORCID account to their PNAS account at \href{http://www.pnascentral.org/}{www.pnascentral.org}. For proper authentication, authors must provide their ORCID at submission and are not permitted to add ORCIDs on proofs.

\subsection*{Submitting Manuscripts}

All authors must submit their articles at \href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you are using Overleaf to write your article, you can use the ``Submit to PNAS'' option in the top bar of the editor window.

\subsection*{Format}

Many authors find it useful to organize their manuscripts with the following order of sections: title, author line and affiliations, keywords, abstract, introduction, results, discussion, materials and methods, acknowledgments, and references. Other orders and headings are permitted.

\subsection*{Manuscript Length}

Brief Reports are limited to 3 pages, which is approximately 1,600 words (including the manuscript text, title page, abstract, and figure legends), and 15 references. Supporting information (SI) is limited to extended methods, essential supporting datasets, and videos (no additional tables or figures).

\subsection*{References}

References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric,phdthesis,masterthesis}. All references cited in the main text should be included in the main manuscript file.

\subsection*{Data Archival}

PNAS must be able to archive the data essential to a published article. Where such archiving is not possible, deposition of data in public databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata, and others outlined in the \href{https://www.pnas.org/author-center/editorial-and-journal-policies#materials-and-data-availability}{Information for Authors}, is acceptable.

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at https://www.pnas.org/author-center/language-editing). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}[t!]
\centering
\includegraphics[width=.8\linewidth]{frog}
\caption{Placeholder image of a frog with a long example legend to show justification setting.}
\label{fig:frog}
\end{figure}

\begin{SCfigure*}[\sidecaptionrelwidth][t]
\centering
\includegraphics[width=11.4cm,height=11.4cm]{frog}
\caption{This legend would be placed at the side of the figure, rather than below it.}\label{fig:side}
\end{SCfigure*}

\begin{table}[t!]
\centering
\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}

\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

\subsection*{Digital Figures}

EPS, high-resolution PDF, and PowerPoint are preferred formats for figures that will be used in the main manuscript. Authors may submit PRC or U3D files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format. Color images must be in RGB (red, green, blue) mode. Include the font files for any text.

Images must be provided at final size, preferably 1 column width (8.7cm). Figures wider than 1 column should be sized to 11.4cm or 17.8cm wide. Numbers, letters, and symbols should be no smaller than 6 points (2mm) and no larger than 12 points (6mm) after reduction and must be consistent.

Figures and tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

Figure \ref{fig:frog} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide. Use \verb|\begin{SCfigure*}...\end{SCfigure*}| for a wide figure with side legends.

\subsection*{Tables}
Tables should be included in the main manuscript file and should not be uploaded separately.

\subsection*{Single column equations}

Authors may use 1- or 2-column equations in their article, according to their preference.

To allow an equation to span both columns, use the \verb|\begin{figure*}...\end{figure*}| environment mentioned above for figures.

Note that the use of the \verb|widetext| environment for equations is not recommended, and should not be used.

\begin{figure*}[bt!]
\begin{align*}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \numberthis \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3.
\end{align*}
\end{figure*}

\subsection*{Supporting Information (SI)}

Authors are limited to the following types of SI: extended methods, datasets, videos, and 3D figures. Extended discussion is not permitted.

\subsection*{SI Appendix}

Supply extended materials and methods information in a separate SI Appendix PDF file. Include SI movie legends. SI will be published as provided by the authors; it will not be edited or composed. Supplementary figures and tables are not allowed.

\subsubsection*{SI Datasets}

Supply .xlsx, .csv, .txt, .rtf, or .pdf files. This file type will be published in raw format and will not be edited or composed.

\subsubsection*{SI Movies}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and and include a brief legend for each movie in the main manuscript file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.

@@

\bibsplit[3]
%Use \bibsplit to split the references from the body of the text. Value "[3]" represents the number of reference in the left column (Note: Please avoid single column figures & tables on this page.)

% Bibliography
\bibliography{pnas-sample}

\end{document}

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1,2]{Susan Vanderplas}
\author[b, c]{Alicia Carriquiry}
\author[b, c, 1]{Heike Hofmann}

\affil[a]{Statistics Department, University of Nebraska Lincoln. 350 Hardin Hall, 3310 Holdrege North Wing, Lincoln, NE 68503}
\affil[b]{Department of Statistics, Iowa State University. 1121 Snedecor Hall, 2438 Osborn Dr, Ames, IA 50011}
\affil[c]{Center for Statistics and Applications in Forensic Evidence. 195 Durham Center, 613 Morrill Road, Ames, Iowa 50011}

% Please give the surname of the lead author for the running footer
\leadauthor{Vanderplas}

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\equalauthors{\textsuperscript{1}SVP (Author One) contributed equally to this work with HH (Author Two).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: susan.vanderplas@unl.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol
\keywords{Forensic Evidence $|$ Statistics $|$ Wire cuts $|$ Toolmark analysis}

@@

Multiple comparisons are a persistent problem for statistical methods and for science more generally. XXX cite XXX In forensic statistics, we have been focusing on the necessity of building up research databases which can be used to develop objective algorithms for evidence comparisons and explore closest non-matches as suggested in \cite{pcast}. While these databases (and open data more generally) are critically important, we also need to be careful about how our methods are affected by the multiple comparison problem.

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we need to be aware of the fact that we often are conducting many comparisons, either implicitly or explicitly. Algorithms in pattern evidence often utilize cross-correlation \cite{vorburgerApplicationsCrosscorrelationFunctions2011} to align different data sources, implicitly making comparisons along the entire length or surface of the data. Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. When we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

Partial matches in fingerprint evidence have been shown to be problematic XXX cite XXX, and the AFIS database search conducted while investigating the Madrid bombing in 2004 was one factor cited in the inquiry into the false accusation of Brandon Mayfield. As forensic intelligence databases in other disciplines are implemented (such as IBIS in firearms), we must confront the issues with multiple comparisons and false positive rates before more embarrasing false accusations lead the public to question the validity of forensic science.

\section*{Calculating the Number of Comparisons}

% Note: please start your introduction without including the word ``Introduction'' as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraph.

% \section*{Guide to using this template on Overleaf}
%
% Please note that whilst this template provides a preview of the typeset manuscript for submission, to help in this preparation, it will not necessarily be the final publication layout. For more detailed information please see the \href{ https://www.pnas.org/page/authors/format}{PNAS Information for Authors}.
%
% If you have a question while using this template on Overleaf, please use the help menu (``?'') on the top bar to search for \href{https://www.overleaf.com/help}{help and tutorials}. You can also \href{https://www.overleaf.com/contact}{contact the Overleaf support team} at any time with specific questions about your manuscript or feedback on the template.
%
% \subsection*{Author Affiliations}
%
% Include department, institution, and complete address, with the ZIP/postal code, for each author. Use lower case letters to match authors with institutions, as shown in the example. PNAS strongly encourages authors to supply an \href{https://orcid.org/}{ORCID identifier} for each author. Individual authors must link their ORCID account to their PNAS account at \href{http://www.pnascentral.org/}{www.pnascentral.org}. For proper authentication, authors must provide their ORCID at submission and are not permitted to add ORCIDs on proofs.
%
% \subsection*{Submitting Manuscripts}
%
% All authors must submit their articles at \href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you are using Overleaf to write your article, you can use the ``Submit to PNAS'' option in the top bar of the editor window.
%
% \subsection*{Format}
%
% Many authors find it useful to organize their manuscripts with the following order of sections: title, author line and affiliations, keywords, abstract, introduction, results, discussion, materials and methods, acknowledgments, and references. Other orders and headings are permitted.
%
% \subsection*{Manuscript Length}
%
% Brief Reports are limited to 3 pages, which is approximately 1,600 words (including the manuscript text, title page, abstract, and figure legends), and 15 references. Supporting information (SI) is limited to extended methods, essential supporting datasets, and videos (no additional tables or figures).
%
%
% \subsection*{References}
%
% References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric,phdthesis,masterthesis}. All references cited in the main text should be included in the main manuscript file.
%
% \subsection*{Data Archival}
%
% PNAS must be able to archive the data essential to a published article. Where such archiving is not possible, deposition of data in public databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata, and others outlined in the \href{https://www.pnas.org/author-center/editorial-and-journal-policies#materials-and-data-availability}{Information for Authors}, is acceptable.
%
% \subsection*{Language-Editing Services}
% Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at https://www.pnas.org/author-center/language-editing). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.
%
% \begin{figure}[t!]
% \centering
% \includegraphics[width=.8\linewidth]{frog}
% \caption{Placeholder image of a frog with a long example legend to show justification setting.}
% \label{fig:frog}
% \end{figure}
%
%
% \begin{SCfigure*}[\sidecaptionrelwidth][t]
% \centering
% \includegraphics[width=11.4cm,height=11.4cm]{frog}
% \caption{This legend would be placed at the side of the figure, rather than below it.}\label{fig:side}
% \end{SCfigure*}
%
% \begin{table}[t!]
% \centering
% \caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
% \begin{tabular}{lrrr}
% Species & CBS & CV & G3 \\
% \midrule
% 1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
% 2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
% 3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
% \bottomrule
% \end{tabular}
%
% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
% \end{table}
%
%
% \subsection*{Digital Figures}
%
% EPS, high-resolution PDF, and PowerPoint are preferred formats for figures that will be used in the main manuscript. Authors may submit PRC or U3D files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format. Color images must be in RGB (red, green, blue) mode. Include the font files for any text.
%
% Images must be provided at final size, preferably 1 column width (8.7cm). Figures wider than 1 column should be sized to 11.4cm or 17.8cm wide. Numbers, letters, and symbols should be no smaller than 6 points (2mm) and no larger than 12 points (6mm) after reduction and must be consistent.
%
% Figures and tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.
%
% Figure \ref{fig:frog} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide. Use \verb|\begin{SCfigure*}...\end{SCfigure*}| for a wide figure with side legends.
%
% \subsection*{Tables}
% Tables should be included in the main manuscript file and should not be uploaded separately.
%
% \subsection*{Single column equations}
%
% Authors may use 1- or 2-column equations in their article, according to their preference.
%
% To allow an equation to span both columns, use the \verb|\begin{figure*}...\end{figure*}| environment mentioned above for figures.
%
% Note that the use of the \verb|widetext| environment for equations is not recommended, and should not be used.
%
% \begin{figure*}[bt!]
% \begin{align*}
% (x+y)^3&=(x+y)(x+y)^2\\
%        &=(x+y)(x^2+2xy+y^2) \numberthis \label{eqn:example} \\
%        &=x^3+3x^2y+3xy^3+x^3.
% \end{align*}
% \end{figure*}
%
%
%
% \subsection*{Supporting Information (SI)}
%
% Authors are limited to the following types of SI: extended methods, datasets, videos, and 3D figures. Extended discussion is not permitted.
%
% \subsection*{SI Appendix}
%
% Supply extended materials and methods information in a separate SI Appendix PDF file. Include SI movie legends. SI will be published as provided by the authors; it will not be edited or composed. Supplementary figures and tables are not allowed.
%
%
% \subsubsection*{SI Datasets}
%
% Supply .xlsx, .csv, .txt, .rtf, or .pdf files. This file type will be published in raw format and will not be edited or composed.
%
%
% \subsubsection*{SI Movies}
%
% Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and and include a brief legend for each movie in the main manuscript file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.
%
%
%
%

@@

\bibsplit[3]
% %Use \bibsplit to split the references from the body of the text. Value "[3]" represents the number of reference in the left column (Note: Please avoid single column figures & tables on this page.)

% Bibliography
% \bibliography{pnas-sample}

\bibliography{../references}
\end{document}
